A demonstration of the \LaTeXe\ class file for \itshape{\journalnamelc}\footnotemark[2]

### 2019-01-27 journal/experiments.tex
done
data location, put threats in own section

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    \end{subfigure}
    \caption{Discovery curves compared to best curves from Chen et. al PLDI 2013 data (FPF benchmark)}
\end{figure*}

@@

\subsection{Threats to Validity}

The largest threat to validity is that this paper's core conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into the data.  In order to check for these problems, we will make the raw data for a re-analysis available on request.

>>>>

\begin{figure}
    \centering
        \includegraphics[width=1.0\textwidth]{jscurve}
        \caption{Discovery curves for SpiderMonkey 1.6 faults}
        \label{jscurves}
 \end{figure}%
    ~ 
    \begin{figure}
        \centering
        \includegraphics[width=1.0\textwidth]{gcccurve}
        \caption{Discovery curves for GCC 4.3.0 wrong-code faults}
        \label{gcccurves}
    \caption{Discovery curves compared to best curves from Chen et. al PLDI 2013 data (FPF benchmark)}
\end{figure}

@@

\section{Threats to Validity}

The largest threat to validity is that this paper's core conclusions rely on only two data sets for compilers, and a small number of non-compiler faults.  The compiler ground truths are possibly imperfect, due to the complex change history, and it was not possible to produce good patches for all faults, limiting our analysis of compiler fault localization.    The comparison with other fault localization methods is also limited:  our compiler experiments limit the mutation budget in ways that may weaken MUSE and MUSEUM effectiveness, and the results using fault and mutant data sets from other studies provide few faults, no multi-fault problems, and very few multi-failure problems, limiting {\bf Repair} effectiveness.   It is also possible that faults in the framework used for experiments introduced errors into our results.  In order to make it possible to check for these problems, we have made the raw data for a re-analysis available: \url{https://github.com/agroce/mutants16/tree/master/tests}.  The data required for analysis of the non-compiler faults is available from the authors of the respective studies (see the acknowledgements at the end of the paper).
